---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(topomatch)
```
# topomatch

Helper function for matching toponyms from different sources, that can
be written in slightly different ways. Allows to inspect the matching
and act accordingly.

```{r example}
countries1 <- raster::ccodes()$NAME
countries2 <- unique(maps::world.cities$country.etc)

(country_matches <- topomatch(countries1, countries2))

str(country_matches)
```


Wraps local-global alignment algorithm borrwed from bioConductor
package `Biostrings`. Works better than global alignment and requires
less fine-tuning (although is considerably slower too)
https://ro-che.info/articles/2016-12-11-local-alignment. 

## Installation

```r
remotes::install_github("Cirad-ASTRE/topomatch")
```

<!-- You can install the released version of topomatch from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("topomatch") -->
<!-- ``` -->
